### 2021-09-23 documentos/math.tex
Choi_N_Partial

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\mu}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\mu=0}^{3} \alpha_{\mu} \ket{\sigma_{\mu}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \dyad{\sigma_{\mu}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\mu}}}{{\sigma_{\mu'}}} = \tr \left(\sigma_{\mu}^{\dagger} \sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$. After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \sigma_{\mu} \otimes \sigma_{\mu}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\mu}=\sqrt{\frac{\tau_{\mu}}{2}}\sigma_{\mu}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\nu} = \frac{1}{2}\sum_{\mu=0}^3H_{\nu\mu}^{(4)}\tau_{\mu},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}
% 
(Proofs in an appendix using binary indices XD)

@@

\subsubsection{$N$ qubits}

Coming soon...

>>>>

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\alpha=0}^{3} \alpha_{\alpha} \ket{\sigma_{\alpha}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \dyad{\sigma_{\alpha}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\alpha}=\sqrt{\frac{\tau_{\alpha}}{2}}\sigma_{\alpha}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\beta} = \frac{1}{2}\sum_{\alpha=0}^3H_{\beta\alpha}^{(4)}\tau_{\alpha},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}

% For the sake of simplicity in the derivation of the relations, let us employ a set of binary indices
% 
% \begin{equation}
% \rho=\sum_{mn=0}^{1} \alpha_{mn} \sigma_{mn},
% % \label{rho}
% \end{equation}

\subsubsection{$N$ qubits}
% 
For the case of $N$ qubits, the density matrix may be written as
% 
\begin{equation}
\rho=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
% \label{rho2}
\end{equation}
% 
Analogously to the single qubit case, we can define a $N$-qubits Pauli map
% 
\begin{equation}
\rho \to \rho'=\mathcal{E}[\rho ]=\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% \label{Pauli_Map}
\end{equation}
% 
with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% 
In this case the density matrix in vector form holds 
% 
\begin{equation}
 \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
\end{equation}
% 
where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
(Proofs in an appendix using binary indices XD)

@@

% \subsubsection{$N$ qubits}
